---
title: "Heartsteps Effect Size"
author: 
date: 
output: 
    beamer_presentation:
      colortheme: "dove"
      toc: false
      incremental: false
      fig_width: 6
      fig_height: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gridExtra)
library(knitr)
library(grid)
library(reshape2)
library(geepack)
library(Matrix)

source('../init.R', chdir=TRUE)
source('../xgeepack.R')
if (!exists('suggest')){
  load(paste(sys.var$mbox.data,'csv.RData',sep=''))
  load(paste(sys.var$mbox.data,"analysis.RData",sep=''))
}

gridline <- element_line(color='lightgrey',linetype='dashed')
ptheme <-
  theme_bw(base_size = 11) +
  theme(panel.grid.major.x=gridline,
        panel.grid.minor.x=element_blank(),
        panel.grid.major.y=gridline,
        panel.grid.minor.y=element_blank(),
        strip.background=element_rect(fill=NA,color='white'),
        legend.position='right',
        legend.direction='vertical')
```


```{r data, echo=FALSE}

unavail_sent_slots <-
            filter(suggest, !avail & !is.na(notification.message))%>%
                select(user, study.day.nogap, slot, avail, notification.message) %>%
  mutate('Message sent' = !is.na(notification.message)) %>% select(-notification.message) %>%
  rename('User' = user, 'Non-travel study day'= study.day.nogap,
         'Decision slot' = slot, 'Available' = avail)
no_message_tag <- 
            filter(suggest, send & !travel & study.day.nogap <= 42 & is.na(send.sedentary)) %>%
                select(user, study.day.nogap, slot, 
                      notification.message) %>%
  rename('User' = user,
         'Non-travel study day' = study.day.nogap,
         'Decision slot' = slot,
         'Sent mesasge' = notification.message)

ntravel <- sum(suggest$travel)
npost41 <- with(suggest, sum(study.day.nogap > 41, na.rm=T))
nexclude <- 
  ntravel + npost41 + nrow(unavail_sent_slots) + nrow(no_message_tag)

suggest.included <- 
  suggest %>%
  filter(!travel & study.day.nogap <= 41) %>%
  anti_join(mutate(no_message_tag, no_message_tag = T),
            by=c('user'='User','study.day.nogap'='Non-travel study day',
                 'slot'='Decision slot')) %>%
  anti_join(mutate(unavail_sent_slots, unavail_sent_slots = T),
            by=c('user'='User','study.day.nogap'='Non-travel study day',
                 'slot'='Decision slot'))

navail <- sum(suggest.included$avail)

# jbsteps30.zero is the zero-imputed raw step count in the 30 minutes after decision
# jbsteps30.log = log(jbsteps30.zero + 0.5)
# jbsteps30pre.zero is the zero-imputed raw step count in the 30 minutes prior to decision
# jbsteps30pre.log = log(jbsteps30pre.zero + 0.5)
# A_t = send
suggest.analysis <-
  suggest.included %>%
    arrange(user, study.day.nogap, decision.index.nogap)

```

```{r effect-calcs, echo=FALSE}


timepoints <-
  with(suggest.analysis, sort(unique(decision.index.nogap)))

s2_yt <-
  suggest.analysis %>%
  filter(avail) %>% # available only
  group_by(decision.index.nogap, send) %>%
  summarise(s2t = var(jbsteps30.log)) %>% # zero imputed, log(steps + 0.5)
  mutate(tm1 = decision.index.nogap - 1)

ybar_t <- 
  suggest.analysis %>%
  filter(avail) %>%
  group_by(decision.index.nogap) %>%
  summarise(ybar1 = mean(jbsteps30.log[which(send)]),
            ybar0 = mean(jbsteps30.log[which(!send)])) %>%
  mutate(ybardiff = ybar1 - ybar0,
         tm1 = decision.index.nogap - 1)

s2pool_t <- 
  suggest.analysis %>%
  filter(avail) %>%
  group_by(decision.index.nogap) %>%
  summarise(s2 = var(jbsteps30.log))

s2pool <-
  with(filter(s2pool_t, decision.index.nogap > 0),
       mean(s2))

```


## Effect size for a difference in means

In general, $\text{effect size} = \text{test statistic} \times \text{study size}$.

E.g. Cohen's $d$:
$$
\begin{aligned} 
d &= \frac{\overline{x}_1 - \overline{x}_2}{s_{\text{pooled}}} \\
t &= d \times \sqrt{\frac{n_1n_2}{n_1+n_2}}
\end{aligned}
$$

## Proximal main effect

$$ \beta(t) = \mathrm{E}\left[\left.Y_{t+1}^{(A_t=1\ldots)} - Y_{t+1}^{(A_t=0\ldots)} \right|I_t=1\right]$$

Assuming it's a smooth function of time.

## Standardized effect in the sample size calculation

$H_1: \beta(t) / \overline{\sigma} = d(t) = \text{standardized effect}$

\vspace{12pt}

Average variance: $\overline{\sigma}^2 = \frac{1}{T} \sum_{t=1}^T \mathrm{E}\left[\mathrm{Var}\left(Y_{t+1} | I_t=1, A_t\right)\right]$

## Estimate $\beta(t)$

with $\overline{Y}^{(A_t=1)}_{t+1} - \overline{Y}^{(A_t=0)}_{t+1}$ (available subjects only)

## Difference in sample means over time

```{r plot-means-time, echo=FALSE}

p.ybar.time <- 
  data.frame(t=timepoints) %>%
  left_join(ybar_t, by=c('t'='tm1')) %>%
  filter(!is.na(ybar1)) %>%
  ggplot(aes(x=t, y=ybardiff)) +
  geom_point(shape=1) +
  ptheme + xlab(expression(t)) + ylab(expression(bar(y)[t+1]^(A[t]==1) - bar(y)[t+1]^(A[t]==0)))
p.ybar.time

```

## Smooth $\hat{\beta}(t)$

```{r smooth-data, echo=FALSE}

nsmooth <- 150
ybar_smooth <-
  expand.grid(t=seq(0, max(timepoints), length.out=nsmooth),
              bwidth = c(10,20)) %>%
  group_by(bwidth) %>%
  mutate(ysmooth = with(filter(ybar_t, tm1>=0),
                        ksmooth(tm1, ybardiff,
                                kernel='normal', x.points=t,
                                bandwidth=unique(bwidth))[['y']]),
         ysmooth_std = with(filter(ybar_t, tm1 >= 0),
                            ksmooth(tm1, ybardiff / sqrt(s2pool),
                                    kernel='normal', x.points=t,
                                    bandwidth=unique(bwidth))[['y']]))

```

```{r smooth-plot-gaussian, echo=FALSE}
ybar_smooth %>% ungroup %>%
  filter(bwidth==20) %>% 
  ggplot(aes(x=t, y=ysmooth)) +
  geom_line() +
  geom_point(aes(x=tm1, y=ybardiff), data=filter(ybar_t, tm1>=0),
             shape=1)+ 
  ptheme + xlab('t') +
  ylab(expression(bar(y)[t+1]^(A[t]==1) - bar(y)[t+1]^(A[t]==0)))

```

## Standardize by...

SD pooled over time and treatment group? 

$\hat{\overline{\sigma}}^2 = \sqrt{\frac{1}{T}\sum \hat{\mathrm{Var}}(Y_{t+1} | I_t=1)}$

## Variances over time

```{r plot-var-time, echo=FALSE, fig.width=6,fig.height=4.5}

data.frame(t=timepoints) %>%
  left_join(s2_yt, by=c('t'='tm1')) %>%
  filter(!is.na(s2t)) %>%
  ggplot(aes(x=t, y=s2t)) + geom_point(aes(color=send), shape=1) +
  ptheme + scale_color_brewer(palette='Dark2',
                              name='',
                              breaks=c('FALSE','TRUE'),
                              labels=c('No suggestion','Suggestion')) +
  theme(legend.position='bottom') +
  ylab('Sample variance at t+1') 
```


## Ratio of variances for each treatment group
```{r plot-sd-ratio-time, echo=FALSE}

data.frame(t=timepoints) %>%
  left_join(s2_yt, by=c('t'='tm1')) %>%
  filter(!is.na(s2t)) %>%
  dcast(t ~ send, value.var='s2t') %>% 
  rename(s2_1 = `TRUE`, s2_0 = `FALSE`) %>%
  ggplot(aes(x=t, y= s2_1 / s2_0)) + 
  geom_point(shape=1) +
  ptheme + xlab(expression(t)) + ylab('ratio of sample variances at t+1')
  #ggtitle('Comparing variances for treated/untreated')

```


## Divide the smoother by the pooled SD

```{r plot-smooth-gauss-std, echo=FALSE}

ybar_smooth %>% ungroup %>%
  filter(bwidth==20) %>% 
  ggplot(aes(x=t, y=ysmooth_std)) +
  geom_line() +
  geom_point(aes(x=tm1, y=ybardiff / sqrt(s2pool)), data=filter(ybar_t, tm1>=0),
             shape=1)+ 
  ptheme + xlab('t') + 
  ylab(expression(frac(bar(y)[t+1]^(A[t]==1) - bar(y)[t+1]^(A[t]==0), s[plain(pool)])))

```

## Issues

- Assumptions for kernel smoother CI
- Interpretable?
- Do I need a ratio CI?
