---
title: "Additonal Moderators"
author: "Brook Luers"
date: "`r format(Sys.time(), '%B %d, %Y')`"
linestretch: 1.5
output: pdf_document
---

```{r setup, echo=FALSE, message=FALSE,warning=FALSE,results='hide'}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gridExtra)
library(knitr)
library(grid)
library(reshape2)
library(geepack)
library(Matrix)


source('../init.R', chdir=TRUE)
if (!exists('suggest')){
  load(paste(sys.var$mbox.data,'csv.RData',sep=''))
  load(paste(sys.var$mbox.data,"analysis-small.RData",sep=''))
}
gridline <- element_line(color='lightgrey',linetype='dashed')
ptheme <-
  theme_bw(base_size = 11) +
  theme(panel.grid.major.x=gridline,
        panel.grid.minor.x=element_blank(),
        panel.grid.major.y=gridline,
        panel.grid.minor.y=element_blank(),
        strip.background=element_rect(fill=NA,color='white'),
        legend.position='right',
        legend.direction='vertical', text=element_text(color='black'))

source('make_new_moderators_Jan.R')
```

See `moderator_analyses.pdf` for all definitions of moderator variables.

## Missingness of thumbs up/down

Out of `r sum(with(suggest.analysis,send==TRUE))` decision points when a message was sent.

```{r, thumbs-summary}

thumbcounts <-
  xtabs(~response+avail, data=suggest.analysis, subset=send==TRUE,
        exclude=NULL, na.action=NULL)

kable(cbind(thumbcounts, round(thumbcounts /sum(thumbcounts),4)),
      col.names=c('Number decision points','Proportion'))

```

## Proportion of sent messages with a "thumbs" response

Denominator: number of prior decision points for which a suggestion message was sent and the response is non-missing.

Numerator: number of prior decision points for which a suggestion message was sent and the response is thumbs up ("good") or thumbs down ("bad").

When the denominator is zero, set the proportion equal to zero.

```{r, plot-prop-updown,fig.align='center',fig.width=6,fig.height=3,out.width='0.75\\textwidth',fig.cap='Proportion of past messages where a suggestion was sent and the user responded thumbs up or thumbs down.'}
suggest.analysis %>%
  #filter(user==10) %>%
  ggplot()+
  geom_line(aes(x=decision.index.nogap,y=prop_prev_thumbs_updown,
                group=user),alpha=I(1/3)) +
  ptheme + xlab('Decision point') + ylab('Proportion of prior messages\nwith up/down response')

```

### Sliding window

Compute the same proportion using a sliding `r ndays_window_thumbs`-day window, including the current day. 
The window slides on the day scale even though the proportion changes on the decision point scale.
Here's an example of how the proportion is calculated for a single user.

```{r, fig.align='center',fig.width=8.5,fig.height=5.5,out.width='0.9\\textwidth',fig.cap='Example of calculation for past 7-day proportion of suggestion messages where the user responded either thumbs up or thumbs down.'}
suggest.analysis %>%
  filter(user==6,study.day.nogap %in% 0:8) %>%
  select(user,decision.index.nogap,denominator=n_prev_sent_have_response,
         numerator=n_prev_thumbs_updown,study.day.nogap,
         window_denominator=n_window_sent_have_response,
         window_numerator=n_window_thumbs_updown) %>%
  melt(id=c('user','decision.index.nogap','study.day.nogap'))%>%
  ggplot(aes(x=decision.index.nogap,y=value))+
  geom_line() + geom_point()+ facet_grid(variable~.) +
  geom_vline(aes(xintercept=decision.index.nogap),
             data=filter(suggest.analysis,user==6,study.day.nogap %in%0:8,slot==1))+
  scale_y_continuous(breaks=seq(0,16,by=2)) +
  xlab('Decision point') + ylab('number of decision points') +
  ptheme +
  theme(panel.grid.major=element_blank()) +
  ggtitle('Top two lines: numerator and denominator for cumulative proportion\nbottom two lines: numerator and denominator in previous 7-day window')
```

```{r,fig.width=6,fig.height=4,out.width='0.75\\textwidth',fig.cap='Past 7-day proportion of suggestion messages where the user responded either thumbs up or thumbs down.'}
suggest.analysis %>%
  #filter(user==10) %>%
  ggplot()+
  geom_line(aes(x=decision.index.nogap,y=prop_window_thumbs_updown,
                group=user),alpha=I(1/3)) +
  ptheme + xlab('Decision point') + ylab('Proportion of prior messages\nwith up/down response')+
  ggtitle(paste("Sliding ",ndays_window_thumbs,'-day window',sep=''))
```



```{r,eval=FALSE,include=FALSE,fig.width=9,fig.height=3.5,out.width='0.9\\textwidth',fig.align='center',fig.cap='Exponentially weighted past 7-day proportion of thumbs up or down ACTIVE messages for a few users.'}
suggest.analysis %>%
  filter(user %in% c(1,10,14)) %>%
  select(user,decision.index.nogap,prop_window_active_thumbs_updown,
         prop_window_active_thumbs_exp05, prop_window_active_thumbs_exp1) %>%
  melt(id=c('user','decision.index.nogap'))%>%
  mutate(user = factor(user,levels=c(1,10,14),
                       labels=c('User 1','10','14')))%>%
  ggplot(aes(x=decision.index.nogap,y=value)) +
  geom_line(aes(color=variable)) +
  facet_wrap(~user) +
  scale_color_brewer(palette='Set1',name='') +
  ptheme +
  theme(legend.position=c(1,0),legend.justification=c(1,0))+
  xlab('Decision point') + ylab('')
```

## Message dose 

The number of messages sent in the past 5, 10, or 25 decision points (moving window). Roughly corresponds to number of messages sent in the last 1, 2, or 5 days. Excludes the current decision point.

```{r, fig.width=9,fig.height=3.5,out.width='0.9\\textwidth',fig.align='center',fig.cap='Number of messages sent in the past 5, 10, and 25 decision points for a few users.'}
suggest.analysis %>%
  filter(user %in% c(1,10,14,15,30)) %>%
  select(user,decision.index.nogap,dose_sent_5points,
         dose_sent_10points,dose_sent_25points) %>%
  melt(id=c('user','decision.index.nogap'))%>%
  mutate(user = factor(user,levels=c(1,10,14,15,30),
                       labels=c('User 1','10','14','15','30')))%>%
  ggplot(aes(x=decision.index.nogap,y=value)) +
  geom_line(aes(color=variable)) +
  facet_wrap(~user) +
  scale_color_brewer(palette='Set1',name='') +
  ptheme +
  theme(legend.position=c(1,0),legend.justification=c(1,0))+
  xlab('Decision point') + ylab('')
```

## Step count in the last 7 days

* Using the "perceived day" step count (e.g. if someone travels from Ann Arbor to Chicago, their perceived day is 25 hours long). 
* Days with missing daily step counts contribute 0 to the cumulative step count.
* Exclude the current day.
* Take the square root of the number of steps in the last 7 days.

```{r,fig.align='center',fig.width=7,fig.height=4,out.width='0.8\\textwidth',fig.cap='Example calculation of total step count in the last 7 days.'}
suggest.analysis %>%
  filter(user==5,study.day.nogap%in%0:12) %>%
  ggplot(aes(x=decision.index.nogap,y=daily.csteps.direct.NA0)) +
  geom_line() +
  geom_line(aes(x=decision.index.nogap,y=steps.window7),
            color='red')+geom_point()+
  geom_vline(aes(xintercept=decision.index.nogap),
             color='grey',
             data=filter(suggest.analysis,user==5,study.day.nogap%in%0:12,slot==1)) + 
  ptheme +
  theme(panel.grid.major.x=element_blank(),
        panel.grid.minor=element_blank()) +
  ggtitle('User 5\nRed line = steps in previous 7 days\nblack line = cumulative steps')+
  ylab('steps') 
```

```{r, fig.width=9,fig.height=3.5,out.width='0.9\\textwidth',fig.align='center',fig.cap='Square root of total number steps in previous 7 days; exponentially discounted moving average of daily square root step count with $\\alpha=0.4$ and $\\alpha=0.8$.'}
suggest.analysis %>%
  filter(user %in% c(1,10,14,15,30)) %>%
  select(user,decision.index.nogap,sqrt.steps.window7,
         daily.sqrt.steps.exp4, 
         daily.sqrt.steps.exp8) %>%
  melt(id=c('user','decision.index.nogap'))%>%
  mutate(user = factor(user,levels=c(1,10,14,15,30),
                       labels=c('User 1','10','14','15','30')))%>%
  ggplot(aes(x=decision.index.nogap,y=value)) +
  geom_line(aes(color=variable)) +
  facet_wrap(~user) +
  scale_color_brewer(palette='Set1',name='') +
  ptheme +
  theme(legend.position=c(1,0),legend.justification=c(1,0))+
  xlab('Decision point') + ylab('')
```


## Variance of step count near decision point in last 7 days

* Compute the number of steps in the interval (30 min before $t$, 30 min after $t$). Using the zero-imputed step counts.
* At the $j$th decision point each day ($j=1,2,3,4,5$), compute the variance of the step counts from the previous 7 days in the 1-hour window surrounding the $j$th decision point on those days.
* This variance is NA for study days 0 through 6. On study day 7, the first non-NA value will correspond to the first decision point index from study day 0. E.g. if the first decision point "slot" on day 0 is the evening, $j=5$, then the first non-NA value for this variance will be on study day 7 for decision point $j=5$ (evening).

Table \ref{tab:alldayvar} displays the first and second decision points from the first 9 days for user 1.
```{r,results='asis'}
suggest.analysis %>% filter(user==1,slot%in%c(1,2),study.day.nogap <9) %>%
  ungroup %>%
  select(study.day.nogap,slot,jbsteps30pre.zero,
         jbsteps30.zero,slot.steps60.prepost.zero,
         window7.steps60.var) -> tt

tt <- as.matrix(tt)
colnames(tt) <- c('Study day','Within-day decision index','Steps 30-minutes before','Steps 30-minutes after','Steps in 1-hour centered interval','Variance from previous 7 days')

print(xtable(tt,
             align='rp{0.1\\textwidth}p{0.15\\textwidth}p{0.15\\textwidth}p{0.15\\textwidth}p{0.15\\textwidth}p{0.15\\textwidth}',
             label='tab:alldayvar',
             caption='Example of previous 7-day variance calculation.',
             digits=c(0,0,0,0,0,0,2)),
      include.rownames=F,
      comment=F)
```

To understand Table \ref{tab:alldayvar}, here is how one of the numbers is calculated.

These are the 1-hour centered window step counts for user 1, morning decision point ($j=1$) for the first 7 days:
```{r,echo=FALSE}
with(suggest.analysis %>% filter(user==1,slot==1,study.day.nogap <8),
     slot.steps60.prepost.zero)
```

This is the corresponding variance:
```{r}
var(with(suggest.analysis %>% filter(user==1,slot==1,study.day.nogap <8),
     slot.steps60.prepost.zero))
```

## Location summary

```{r locatble,echo=FALSE,results='asis'}
round(with(suggest.analysis,table(loc.is.work,loc.is.home)) / nrow(suggest.analysis),3) -> tt
colnames(tt) <-c('Not home','Home')
rownames(tt) <-c('Not at work','At work')

print(xtable(tt,
             caption=paste('Decision points classified by location, out of',nrow(suggest.analysis),'total decision points.'),
             label='tab:loc'),
      hline.after=NULL,
      comment=FALSE)

```



## Survey responses

Both data frames (`suggest.analysis` and `suggest.analysis.wdays`) contain the following two variables computed from the intake survey:

* `selfeff_sum`: Self efficacy score. This is the sum of the following columns from the `users` data frame:  `r paste(select(users, starts_with('selfeff')) %>%
  select(-ends_with('exit')) %>%names,collapse=', ')`
* `conc_sum`: Conscientiousness score. This is the sum of the following colmns from the `users` data frame: `r paste(conc_item_names, collapse=', ')`