---
title: "Tracker exploratory analysis"
author: "Brook Luers"
date: "July 18, 2016"
output: html_document
---


```{r setup,echo=FALSE, warning=FALSE, message=FALSE}

library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gridExtra)
library(knitr)
library(grid)
library(reshape2)
library(geepack)
knitr::opts_chunk$set(echo = FALSE)
source('../init.R', chdir=TRUE)
source('../xgeepack.R')
if (!exists('suggest')){
  load(paste(sys.var$mbox.data,'csv.RData',sep=''))
  load(paste(sys.var$mbox.data,"analysis.RData",sep=''))
}

gridline <- element_line(color='lightgrey',linetype='dashed')
ptheme <-
  theme_bw(base_size = 11) +
  theme(panel.grid.major.x=gridline,
        panel.grid.minor.x=element_blank(),
        panel.grid.major.y=gridline,
        panel.grid.minor.y=element_blank(),
        strip.background=element_rect(fill=NA,color='white'),
        legend.position='right',
        legend.direction='vertical')

```


```{r data,echo=FALSE}

unavail_sent_slots <-
            filter(suggest, !avail & !is.na(notification.message))%>%
                select(user, study.day.nogap, slot, avail, notification.message) %>%
  mutate('Message sent' = !is.na(notification.message)) %>% select(-notification.message) %>%
  rename('User' = user, 'Non-travel study day'= study.day.nogap,
         'Decision slot' = slot, 'Available' = avail)
no_message_tag <- 
            filter(suggest, send & !travel & study.day.nogap <= 42 & is.na(send.sedentary)) %>%
                select(user, study.day.nogap, slot, 
                      notification.message) %>%
  rename('User' = user,
         'Non-travel study day' = study.day.nogap,
         'Decision slot' = slot,
         'Sent mesasge' = notification.message)

suggest.included <- 
  suggest %>%
  filter(!travel & study.day.nogap <= 41) %>%
  anti_join(mutate(no_message_tag, no_message_tag = T),
            by=c('user'='User','study.day.nogap'='Non-travel study day',
                 'slot'='Decision slot')) %>%
  anti_join(mutate(unavail_sent_slots, unavail_sent_slots = T),
            by=c('user'='User','study.day.nogap'='Non-travel study day',
                 'slot'='Decision slot'))



keep_users <- sort(unique(suggest.included$user))


tracker.user.day <- 
  daily %>%
  filter(study.day.nogap <= 41 & user %in% keep_users) %>%
  select(user, study.date, study.day.nogap, last.utime, travel) %>%
  group_by(user) %>% mutate(n_days = max(study.day.nogap, na.rm=T) + 1) %>%
  left_join(
    tracker %>%
      group_by(user, start.date) %>%
      summarise(n_starts = n())
    , by=c('user'='user', 'study.date'='start.date')
  ) %>% 
  filter(!travel, study.day.nogap <= 41) %>% 
  group_by(user) %>%
  summarise(n_days = max(n_days),
            n_no_tracker = sum(is.na(n_starts)))

cutoff_hour_first <- 3
tracker.first.app.day <- 
  tracker %>%
  select(user, start.date, start.ltime, duration.secs, app, rank) %>%
  group_by(user, start.date) %>%
  arrange(start.ltime) %>%
  filter(start.ltime >= trunc(start.ltime, 'day') + 60*60*cutoff_hour_first) %>%
  mutate(my_order=order(start.ltime)) %>% 
  filter(my_order==1) %>%
  select(user, start.date, first_ltime = start.ltime, 
         first_app = app) 

daily.first.app <-
  daily %>%
  filter(!travel & user %in% keep_users) %>%
  select(user, study.date, study.day.nogap) %>%
  left_join(tracker.first.app.day,
            by=c('user'='user','study.date'='start.date')) %>%
  mutate(secs_first_use = difftime(first_ltime, trunc(first_ltime, 'day'),
                                     units='secs'),
         secs_first_use_num = as.numeric(secs_first_use))



```

### User-days without app usage data

About `r with(tracker.user.day, round(100*sum(n_no_tracker) / sum(n_days)))` percent (`r sum(tracker.user.day$n_no_tracker)` / `r sum(tracker.user.day$n_days)`) of user-days have no app usage data.

The following users have at least one day without any app usage data:

```{r table-notracker-days, echo=FALSE, results='asis'}

tt <- 
  tracker.user.day %>%
  filter(n_no_tracker>0) %>%
  mutate(prop = n_no_tracker / n_days) %>%
  arrange(desc(prop)) %>%
  select(user, prop)

names(tt) <- c('User','Proportion of study days without tracker data')
tt[,2] <- round(tt[,2],2)
kable(as.data.frame(tt),
      align='r',
      padding=0,
      format='markdown')

```

### Time of first daily phone usage

The following histogram shows times of first daily phone usage according to the tracker data for each user. I defined "time of first usage" as the earliest tracker timestamp that occurred after `r cutoff_hour_first` a.m. 

```{r hist-time-first, echo=FALSE, fig.width=8, fig.height=7}
## Histogram of time of first app usage

breaks_first_use <- 
  with(daily.first.app,
       seq(min(secs_first_use_num, na.rm=T),
         max(secs_first_use_num, na.rm=T),
         by=60*60*6))

labels_first_use <-
  format(as.POSIXct('2016-07-20 00:00:00') + breaks_first_use,
       '%H:%M')

top_app_names <-
  names(
  with(daily.first.app,
     sort(table(first_app), decreasing=T))[1:3]
)

daily.first.app <-
  daily.first.app %>%
  mutate(first_app_f = paste(factor(first_app,
                                    levels=top_app_names)),
         first_app_f = factor(ifelse(first_app_f=='NA', 'Other',first_app_f)))

daily.first.app %>%
  filter(!is.na(secs_first_use_num)) %>%
  mutate(user = factor(user,
                       levels=unique(user),
                       labels=paste(c('User ',rep('',length(unique(user))-1)),
                                    unique(user), sep=''))) %>%
  ggplot(aes(x=secs_first_use_num)) +
  geom_histogram(aes(fill=first_app_f),
                 binwidth=60*60,color=NA) + 
  ptheme +
  scale_x_continuous(breaks = breaks_first_use,
                     labels=as.character(labels_first_use)) +
  facet_wrap(~user, ncol=6) +
  scale_y_continuous(breaks=c(0,10,20)) +
  xlab(paste('Time of first tracker activity\nafter ',cutoff_hour_first,' a.m.',sep='')) +
  ylab('Num. study days') +
  scale_fill_manual(values=c(brewer.pal(length(top_app_names),'Dark2'),
                              'darkgrey'),
                     breaks=c(top_app_names,'Other'),
                    name='') +
  theme(legend.position=c(1,0),
        legend.justification=c(1,0),
        legend.direction='horizontal',
        axis.text.x=element_text(angle=45,hjust=1))

```


### Time since last phone usage (prior to decision point)

```{r time-prior-data, echo=FALSE, include=FALSE, eval=FALSE}

suggest.included %>%
  group_by(user) %>%
  summarise(n_points = n(),
            prop_no_dev_since = sum(is.na(device.since)) / n_points)

suggest.included %>%
  group_by(user) %>%
  mutate(n_points = n(),
            prop_no_dev_since = sum(is.na(device.since)) / n_points) %>%
  filter(prop_no_dev_since <1) %>% ungroup %>%
  ggplot(aes(x=as.numeric(device.since))) + 
  geom_histogram(aes(y=..density..)) + 
  facet_wrap(~user)

```

